For heavy neutral Higgs in models with extended Higgs sectors, such as the MSSM, the decay
to two $\tau$ leptons is dominant at high masses and values of tan$\beta$. The ATLAS collaboration has
performed a search for neutral Higgs bosons decaying to $\tau$ leptons using an integrated luminosity
of 3.2 fb$^{−1}$. The search is performed in two channels, where one $\tau$ decays leptonically and the
other hadronically ($\tau_{\rm lept}$$\tau_{\rm had}$) and where both $\tau$ leptons decay hadronically ($\tau_{\rm had}$$\tau_{\rm had}$) .
In the $\tau_{\rm had}$$\tau_{\rm had}$ channel, multi-jet events form the dominant background, and they are estimated
using a data-driven fake-factor method. Events from other processes with a jet misidentified
as a $\tau_{\rm had}$, such as W+jets and top-quark backgrounds, are taken from simulation and
corrected using fake rates measured from data. Events with correctly identified $\tau_{\rm had}$ are taken
from simulation, with some data-driven corrections to the normalization.
In the $\tau_{\rm lept}$$\tau_{\rm had}$, backgrounds from all processes that involve jets misidentified as $\tau_{\rm had}$
are estimated simultaneously in a data-driven fake-factor method that takes into account the
fractional contribution of the dominant background processes of W+jets and multi-jets. Events
with electrons misidentified as a $\tau_{\rm had}$ are suppressed in the electron channel with a veto on the
visible mass of the $\tau_{\rm had}$ and lepton of the Z boson mass window, $80~{\rm GeV} < m_{\rm vis} < 110~{\rm GeV}$.
The remaining backgrounds are corrected with a data-driven scale factor derived within the Z boson mass window. Backgrounds with a correctly identified $\tau_{\rm had}$ are taken from simulation.
In both channels, the final discriminating variable is 
The final result is provided both as a limit on the cross section times branching ratio as well
as a model-dependent limit on various MSSM benchmark models. The sensitivity exceeds the
8 TeV result for $m_{H} >$ 750 GeV. The limits for all channels combined are shown in Figure 2
for the gluon fusion and b-associated production methods, with the separate expected limits for
the $\tau_{\rm lept}$$\tau_{\rm had}$ and $\tau_{\rm had}$$\tau_{\rm had}$ channels overlaid.